Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-09-11 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_09_10_MK.Rmd
x

# Boxplot showing outliers
ggplot(df_aoi_sum, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of mumber of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()

>>>>

# Boxplot showing outliers
ggplot(df_aoi_sum, aes(x = "", y = Number_fixation_min_mtu)) + 
  geom_boxplot(outlier.color = "red", outlier.shape = 19, outlier.size = 3) +
  labs(title = "Boxplot of number of fixations per minute (micro-teaching unit)",
       y = "Number of fixations per minute") +
  theme_minimal()
